Interim report\\ Measles risk assessment, modelling and cost analysis\\ \vspace{2 mm} {\large David T S Hayman, Tim Carpenter,\\ Jonathan C Marshall, Mick Roberts, Nigel P French}

### 2014-07-07 interimreport1.Rnw
Updated bibliography
No other changes at all

\bibitem[Carabin et al.(2003)]{carabin3}
Carabin, H., W.~J. Edmunds, M. Gyldmark, P. Beutels, D. Lévy-Bruhl, H. Salo, U.~K. and Griffiths (2003)
\newblock The cost of measles in industrialised countries.
\newblock \emph{Vaccine}, 21,4167--4177.

@@

\bibitem[Dayan et al.(2005)]{dayan5}
NA
\newblock The cost of containing one case of measles: the economic impact on the public health infrastructure - Iowa, 2004.
\newblock \emph{Pediatrics}, 116:e1; DOI:10/1542/peds.2004-2512.

@@

\bibitem[Filia et al.(2007)]{filia7}
NA
\newblock Health burden and economic impact of measles-related hospitalization in Italy, 2002-2003.
\newblock \emph{BMC Public Health}, 7,169

@@

\bibitem[Obidia et al.(2012)]{obidia12}
NA
\newblock The R0 package: a toolbox to estimate reproduction numbers for epidemic outbreaks.
\newblock \emph{BMC Medical Informatics and Decision Making}, 2012, 12--147.

\bibitem[Parker et al.(2006)]{parker6}
NA
\newblock Implications of a 2005 measles outbreak in Indiana for sustained elimination of measles in the United States.
\newblock \emph{The New England Journal of Medicine}, 355, 447--455.

@@

\bibitem[Siedler et al.(2006)]{siedler6}
Siedler, A., A. Tischer, A. Mankertz, and S. Santibanez (2006).
\newblock Two outbreaks of measles in Germany 2005.
\newblock \emph{Eurosurveillance} 2006:11(4) article 5, http://www.eurosurveillance.org/ViewArticle.aspx?ArticleId=615, accessed 14 June 2014.

@@

\bibitem[Statistics New Zealand)]{stats14}
\newblock \emph{Statistics New Zealand} (2014).
http://nzdotstat.stats.govt.nz/, accessed 17 June 2014.

>>>>

\bibitem[Carabin et al.(2003)]{carabin3}
Carabin, H., W.~J. Edmunds, M. Gyldmark, P. Beutels, D. Levy-Bruhl, H. Salo, U.~K. and Griffiths (2003)
\newblock The cost of measles in industrialised countries.
\newblock \emph{Vaccine}, 21,4167--4177.

@@

\bibitem[Dayan et al.(2005)]{dayan5}
G.~H. Dayan, I.~R. Ortega-Sanchez, C.~W. LeBaron, M.~P. Quinlisk, and the Iowa Measles Response Team (2005).
\newblock The cost of containing one case of measles: the economic impact on the public health infrastructure - Iowa, 2004.
\newblock \emph{Pediatrics}, 116:e1; DOI:10/1542/peds.2004-2512.

@@

\bibitem[Filia et al.(2007)]{filia7}
Filia, A., A. Brenna, A. Pana, G.~M. Cavallaro, M. Massari and M.~L.C. degli Atti (2007).
\newblock Health burden and economic impact of measles-related hospitalization in Italy, 2002-2003.
\newblock \emph{BMC Public Health}, 7,169

@@

\bibitem[Obidia et al.(2012)]{obidia12}
Obadia, T., R. Haneef and P--Y. Boelle
\newblock The R0 package: a toolbox to estimate reproduction numbers for epidemic outbreaks.
\newblock \emph{BMC Medical Informatics and Decision Making}, 2012, 12--147.

\bibitem[Parker et al.(2006)]{parker6}
Parker, A.~A., W. Staggs, G.~H. Dayan, I.~R. Ortega-Sanchez, P.~A. Rota, L. Lowe, P. Boardman, R. Teclaw, C. Graves, and C.~W. LeBaron (2006).
\newblock Implications of a 2005 measles outbreak in Indiana for sustained elimination of measles in the United States.
\newblock \emph{The New England Journal of Medicine}, 355, 447--455.

@@

\bibitem[Siedler et al.(2006)]{siedler6}
Siedler, A., A. Tischer, A. Mankertz, and S. Santibanez (2006).
\newblock Two outbreaks of measles in Germany 2005.
\newblock \emph{Eurosurveillance} 2006:11(4) article 5, \href{http://www.eurosurveillance.org/ViewArticle.aspx?ArticleId=615}{www.eurosurveillance.org}, accessed 14 June 2014.

@@

\bibitem[Statistics New Zealand(2014))]{stats14}
\newblock \emph{Statistics New Zealand} (2014).
http://nzdotstat.stats.govt.nz/, accessed 17 June 2014.
